XOR-Some Prolific Pilot 2

### 2021-04-10 analysis/xor-some-prolific-pilot2.Rmd
fix fig sizes and adapt_delta

Visually check the spread of by-item ratings among subjects for each question:
```{r, fig.height=20, fig.width=7}

@@

Plot by-item trends between predictor ratings and target inference strength ratings (relevance / competence ratings with utterance are omitted):
```{r, fig.height=20, fig.width=8}
# make a versatile wide representation of the critical data
d_critical_predictorsXtarget <- d_critical_wide %>% 
  pivot_longer(
    cols = c(relevance, prior, competence, relevance_wUtt, competence_wUtt),
    names_to = "predictors",
    values_to = "predictor_response"
  ) %>%
  filter(predictors != "relevance_wUtt", predictors != "competence_wUtt")

@@

Plot inference strength ratings against predictor ratings, by-item, using by-item mean ratings across participants. Error bars indicate the standard deviation of the mean:
```{r, fig.height=4, fig.width=8}
d_critical_predictorsXtarget_summary <- d_critical_predictorsXtarget %>% 
  group_by(title, predictors, main_type) %>%
  summarise(mean_target = mean(target),
            mean_predictor = mean(predictor_response), 
            sd_target = sd(target),
            sd_predictor = sd(predictor_response))

d_critical_predictorsXtarget_summary %>%
  ggplot(., aes(x = mean_predictor, y = mean_target)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_target - sd_target, ymax = mean_target + sd_target), alpha = 0.7) +
  geom_errorbarh(aes(xmin = mean_predictor - sd_predictor, xmax = mean_predictor + sd_predictor), alpha = 0.7) +
  geom_text(aes(label=title), size = 1.5, nudge_y = 4) +
  geom_smooth(method = "lm") +
  ylab("Mean inference strength rating") +
  xlab("Mean predictor ratings") + 
  facet_wrap(main_type~predictors)
```

@@

#### Smaller models with raw data to check for collinearity 
Models on raw data with only one predictor: 
```{r, results='hide'}
# xor
model_xor_prior <- brm(
  target ~ prior + 
    (1 + prior | submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_comp <- brm(
  target ~ competence + 
    (1 + competence | submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_rel <- brm(
  target ~ relevance + 
    (1 + relevance | submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_rel <- brm(
  target ~ relevance + 
    (1 + relevance | submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_prior <- brm(
  target ~ prior + 
    (1 + prior | submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_comp <- brm(
  target ~ competence + 
    (1 + competence | submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "some"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_pri_rel <- brm(
  target ~ prior*relevance + 
    (1 + prior*relevance || submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  cores = 4,
  iter = 3000
)
```

>>>>

Visually check the spread of by-item ratings among subjects for each question:
```{r, fig.height=20, fig.width=10}

@@

Plot by-item trends between predictor ratings and target inference strength ratings (relevance / competence ratings with utterance are omitted):
```{r, fig.height=35, fig.width=15}
# make a versatile wide representation of the critical data
d_critical_predictorsXtarget <- d_critical_wide %>% 
  pivot_longer(
    cols = c(relevance, prior, competence, relevance_wUtt, competence_wUtt),
    names_to = "predictors",
    values_to = "predictor_response"
  ) %>%
  filter(predictors != "relevance_wUtt", predictors != "competence_wUtt")

@@

Plot inference strength ratings against predictor ratings, by-item, using by-item mean ratings across participants. Error bars indicate the standard deviation of the mean:
```{r, fig.height=10, fig.width=8}
d_critical_predictorsXtarget_summary <- d_critical_predictorsXtarget %>% 
  group_by(title, predictors, main_type) %>%
  summarise(mean_target = mean(target),
            mean_predictor = mean(predictor_response), 
            sd_target = sd(target),
            sd_predictor = sd(predictor_response))

d_critical_predictorsXtarget_summary %>%
  ggplot(., aes(x = mean_predictor, y = mean_target)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_target - sd_target, ymax = mean_target + sd_target), alpha = 0.7) +
  geom_errorbarh(aes(xmin = mean_predictor - sd_predictor, xmax = mean_predictor + sd_predictor), alpha = 0.7) +
  geom_text(aes(label=title), size = 2.5, nudge_y = 4) +
  geom_smooth(method = "lm") +
  ylab("Mean inference strength rating") +
  xlab("Mean predictor ratings") + 
  facet_wrap(main_type~predictors)
```

@@

#### Smaller models with raw data to check for collinearity 
Models on raw data with only one predictor: 
```{r, results='hide'}
# xor
model_xor_prior <- brm(
  target ~ prior + 
    (1 + prior | submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  control = list(adapt_delta = 0.99),
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_comp <- brm(
  target ~ competence + 
    (1 + competence | submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  control = list(adapt_delta = 0.99),
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_rel <- brm(
  target ~ relevance + 
    (1 + relevance | submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  control = list(adapt_delta = 0.99),
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_rel <- brm(
  target ~ relevance + 
    (1 + relevance | submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "some"),
  family = "gaussian",
  control = list(adapt_delta = 0.99),
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_prior <- brm(
  target ~ prior + 
    (1 + prior | submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "some"),
  family = "gaussian",
  control = list(adapt_delta = 0.99),
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# some
model_some_comp <- brm(
  target ~ competence + 
    (1 + competence | submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "some"),
  family = "gaussian",
  control = list(adapt_delta = 0.92),
  cores = 4,
  iter = 3000
)
```

@@

```{r, results='hide'}
# xor
model_xor_pri_rel <- brm(
  target ~ prior*relevance + 
    (1 + prior*relevance || submission_id) +
    (1 | title),
  data = d_critical_wide %>% filter(main_type == "xor"),
  family = "gaussian",
  control = list(adapt_delta = 0.92),
  cores = 4,
  iter = 3000
)
```
